Effects of Reynolds Number on the Performance and Near-Wake of a Cross-Flow Turbine

### 2015-03-23 paper.tex
Copy bib file locally
Fix citation keys

%=================================================================
\setcounter{page}{1}
\lastpage{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2014}
\history{Received: xx / Accepted: xx / Published: xx}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

@@

Previously, Bachant and Wosnik \cite{Bachant2014_JOT} showed that a cross-flow
turbine wake's unique mean flow field is responsible for accelerated wake
recovery when compared with conventional axial-flow propeller-type turbines.

@@

Experiments were performed in the University of New Hampshire's tow/wave tank
turbine test bed. The turbine model is dubbed the UNH-RVAT, for Reference
Vertical Axis Turbine, which is designed to be a generic case for numerical
model testing, similar to the Sandia National Labs/US Department of Energy RM2
River Turbine. Details of the turbine and experimental setup are described in
\cite{Bachant2014_JOT}, and a CAD model of the turbine is available from
\cite{Bachant2014_CAD}.

@@

\bibliography{../../../Library/Library}
\bibliographystyle{mdpi}

>>>>

%=================================================================
\setcounter{page}{1}
\lastpage{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2014}
\history{Received: xx / Accepted: xx / Published: xx}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to
%arXiv.org
%\pdfoutput=1

@@

Previously, Bachant and Wosnik \cite{Bachant2015-JoT} showed that a cross-flow
turbine wake's unique mean flow field is responsible for accelerated wake
recovery when compared with conventional axial-flow propeller-type turbines.

@@

Experiments were performed in the University of New Hampshire's tow/wave tank
turbine test bed. The turbine model is dubbed the UNH-RVAT, for Reference
Vertical Axis Turbine, which is designed to be a generic case for numerical
model testing, similar to the Sandia National Labs/US Department of Energy RM2
River Turbine. Details of the turbine and experimental setup are described in
\cite{Bachant2015-JoT}, and a CAD model of the turbine is available from
\cite{Bachant2014-RVAT-CAD}.

@@

\bibliography{library}
\bibliographystyle{mdpi}
